The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
foundational >> seminal/germinal
Fig1 caption

# Abstract
Scale remains a seminal concept in ecology. Spatial scale, for instance, has
become a central consideration in the way we understand landscape ecology and
animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges. Multilayer networks
promise the integration of monolayer animal social networks with the complexity
and importance of animal space use and movement in heterogeneous landscapes.
Despite the complex interplay between social networks and how animals use space,
there remains an important biological and methodological gap in our
understanding of an animal’s perception of scale. But
scale can affect multilayer network dynamics and how we build and interpret
them. Here we discuss the role of scale in the context of multilayer networks
and provide a social ungulate case study to illustrate the role
of social, spatial, and temporal scale on multilayer processes. We also present
perspectives on future development and application of scale in multilayer
networks with respect to: habitat selection and space use; phenotypes and individual fitness; and movement ecology and collective movement. Effective integration
of social and spatial processes, including biologically meaningful scales,
within the context of animal social networks is an emerging area of research;
our contribution incorporates perspectives on how the social
environment and spatial processes are linked across scales in a multilayer

@@

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in the social, spatial, and temporal
improve predictions associated with biological differences in seasonal resource
availability and social association? We conclude with perspectives for further
development and application of scale in multilayer networks with respect to 
phenotypes and individual fitness [@Webber_2018], movement ecology and collective
movement [@Jolles_2019], and habitat selection and space use <!-- TODO: (REF)-->,  and .

(ref:spacetime) Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.

>>>>

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance, has
become a central consideration in the way we understand landscape ecology and
animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges. Multilayer networks
promise the integration of monolayer animal social networks with the complexity
and importance of animal space use and movement in heterogeneous landscapes.
Despite the complex interplay between social networks and how animals use space,
there remains an important biological and methodological gap in our
understanding of an animal’s perception of scale. But
scale can affect multilayer network dynamics and how we build and interpret
them. Here we discuss the role of scale in the context of multilayer networks
and provide a social ungulate case study to illustrate the role
of social, spatial, and temporal scale on multilayer processes. We also present
perspectives on future development and application of scale in multilayer
networks with respect to: habitat selection and space use; phenotypes and individual fitness; and movement ecology and collective movement. Effective integration
of social and spatial processes, including biologically meaningful scales,
within the context of animal social networks is an emerging area of research;
our contribution incorporates perspectives on how the social
environment and spatial processes are linked across scales in a multilayer

@@

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in the social, spatial, and temporal
improve predictions associated with biological differences in seasonal resource
availability and social association? We conclude with perspectives for further
development and application of scale in multilayer networks with respect to 
phenotypes and individual fitness [@Webber_2018], movement ecology and collective
movement [@Jolles_2019], and habitat selection and space use <!-- TODO: (REF)-->.

(ref:spacetime) Space-time diagram displaying variation the relative spatial and temporal extent 
required for different types of social and communication processes for four species, including 
hyaena, passerine birds, sleepy lizards, and elephants. Spatial and temporal extent for social interactions,
e.g. mating, grooming, or aggression, are similar for most species because physical contact between 
two individuals is required for most social interactions. The logical extension is that spatial and temporal extent for
social interaction is nested within the spatial and temporal extent for social association because individuals must 
shared space to interact. By contrast, different species have potential for  greater spatial and 
temporal extents, for example, temporal extent for vocal communication is similar 
for most species because most vocal calls only persist in the environment for seconds, but spatial 
extent for vocal communication is highly variable with elephant calls extending the great distance and 
passerine calls extending the shortest distance.
